CUNY SPSS Data Science Math Homework 3

### 2018-07-26 data-science-math/Homework 3.Rmd
Additional work

```{r}
m <- 1300 
sd <- 40000**(1/2)
x <- 979
z <- (x-m)/sd
round(1-pnorm(z),4)
```

@@

```{r}
m <- 11000 
sd <- 1960000 **(1/2)
x <- 8340
z <- (x-m)/sd
round(1-pnorm(z),4)
round(1-pnorm(x, m, sd), 4)
```

@@

```{r}

```

@@

@@

@@

A research company desires to know the mean consumption of beef per week among males over age 48. Suppose a sample of size 208 is drawn with $\bar{X}$=3.9. Assume å = 0.8 . Construct the 80% confidence interval for the mean number of lb. of beef per week among males over 48. (Round your answers to 1 decimal place)

Lower Bound:

Upper Bound:

@@

An economist wants to estimate the mean per capita income (in thousands of dollars) in a major city in California. Suppose a sample of size 7472 is drawn with $\bar{X}$= 16.6. Assume å = 11 . Construct the 98% confidence interval for the mean per capita income. (Round your answers to 1 decimal place)

Lower Bound:

Upper Bound:

@@

@@

@@

@@

@@

@@

Lower Bound:

Upper Bound:

@@

@@

Lower Bound:

Upper Bound:

@@

@@

@@

@@

Lower Bound:

Upper Bound:

@@

@@

Lower Bound:

Upper Bound:

>>>>

```{r}
m <- 1300 
sd <- sqrt(40000)
x <- 979
z <- (x-m)/sd
round(1-pnorm(z),4)
```

@@

```{r}
m <- 11000 
sd <- sqrt(1960000)
x <- 8340
z <- (x-m)/sd
round(1-pnorm(z),4)
round(1-pnorm(x, m, sd), 4)
```

@@

**0.2307**

$$\mu=N\pi=151\times0.09 = 13.59$$

$$\sigma=\sqrt{N\pi(1-\pi)} = \sqrt{151\times0.09\times 0.91}\approx3.51666$$

$$ Z = \frac{(x-\mu)}{\sigma}=\frac{(11-13.59)}{3.51666}\approx-0.7364942$$

```{r}
N <- 151
n <- 11
p <- 0.09
m <- N * p
sd <- sqrt(N*p*(1-p))
z <- (n-m)/sd
round(pnorm(z),4)
```

@@

$$\mu=N\pi=540\times0.07 = 37.8$$

$$\sigma=\sqrt{N\pi(1-\pi)} = \sqrt{540\times0.07\times 0.93}\approx5.929081$$

$$\bar{x}=N\pi=540\times(0.07-0.03) = 21.6$$
$$ Z = \frac{(\bar{x}-\mu)}{\sigma}=\frac{(21.6-37.8)}{5.929081}\approx-2.732295$$

**0.0031**

```{r}
n <- 540
p <- 0.07
dif <- -0.03
m <- n*p
sd <- sqrt(n*p*(1-p))
x <- n*(p+dif)
z <- (x-m)/sd
round(pnorm(z), 4)
```

@@

**0.0098**

```{r}
n <- 602
p <- 0.23
dif <- 0.04 
m <- n*p
sd <- sqrt(n*p*(1-p))
x <- n*(p+dif)
z <- (x-m)/sd
round(pnorm(z, lower.tail = FALSE), 4)
```

@@

A research company desires to know the mean consumption of beef per week among males over age 48. Suppose a sample of size 208 is drawn with $\bar{X}$=3.9. Assume $\sigma$=0.8. Construct the 80% confidence interval for the mean number of lb. of beef per week among males over 48. (Round your answers to 1 decimal place)

Lower Bound: **3.8**

Upper Bound: **4.0**

I looked up the Z value for 80% in a table which is 1.282.

```{r}
n <- 208
x <- 3.9
sd <- 0.8
sdm <- sd / sqrt(n) 
z <- 1.282

round(x - z * sdm, 1)

round(x + z * sdm, 1)
```

@@

An economist wants to estimate the mean per capita income (in thousands of dollars) in a major city in California. Suppose a sample of size 7472 is drawn with $\bar{X}$= 16.6. Assume $\sigma$= 11 . Construct the 98% confidence interval for the mean per capita income. (Round your answers to 1 decimal place)

Lower Bound: **16.3**

Upper Bound: **16.9**

```{r}
n <- 7472
x <- 16.6
sd <- 11
sdm <- sd / sqrt(n) 
z <- 2.326

round(x - z * sdm, 1)

round(x + z * sdm, 1)
```

@@

```{r echo=FALSE}
library(ggplot2)
funcShaded <- function(x) {
  df <- 26
  y <- dt(x, df)
  t_val <- qt(0.05, df)
  y[x > t_val] <- NA
  return(y)
}
ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
  stat_function(fun = dt, args = list(df = 26)) + 
  stat_function(fun=funcShaded, geom="area", fill="#84CA72", alpha=0.5) + 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```

@@

**-1.705618**

```{r}
qt(0.05, 26)
```

@@

**352.17**

```{r}
obs <- c(383.6, 347.1, 371.9, 347.6, 325.8, 337)
n <- length(obs)
m <- mean(obs)
round(m, 2)
```

@@

**21.68**

```{r}
sdm = sd(obs)
round(sdm, 2)
```

@@

**1.476**

```{r}
df <- n - 1
t <- qt(.9, df)
round(t, 3)
```

@@

Lower Bound: **320.18**

Upper Bound: **384.16**

```{r}
round(m-t*sdm, 2)
round(m+t*sdm, 2)
```

@@

**0.866**

```{r}
n <- 16
m <- 46.4
sdm <- 2.45
df <- n - 1
t <- qt(.8, df)
round(t, 3)
```

@@

Lower Bound: **44.28**

Upper Bound: **48.52**

```{r}
round(m-t*sdm, 2)
round(m+t*sdm, 2)
```

@@

**1417**

```{r}
ci <- 0.99
z <- qnorm(1-(1-ci)/2)
sigma <- 1.9
moe <- 0.13
n <- ((z * sigma)/moe)**2
round(n, 0)
```

@@

**384**

```{r}
m <- 12.6
sigma <- sqrt(3.61)

ci <- 0.95
z <- qnorm(1-(1-ci)/2)
moe <- 0.19
n <- ((z * sigma)/moe)**2
round(n, 0)
```

@@

**35/2089 or 0.170**

$$\frac{2089-1734}{2089} = \frac{355}{2089} \approx 0.170 $$

```{r}
N <- 2089
n <- 1734
p <- (N-n)/N
round(p, 3)
```

@@

Lower Bound: **0.153**

Upper Bound: **0.187**

```{r}
ci <- 0.98
m <- N * p
sdm <- sqrt(N*p*(1-p))

df <- (N-n) - 1
t <- qt(ci, df)
round((m-t*sdm)/N, 3)
round((m+t*sdm)/N, 3)
```

@@

**156/474 or 0.329**

```{r}
N <- 474
n <- 156
p <- n/N
round(p, 3)
```

@@

Lower Bound: **0.294**

Upper Bound: **0.365**

```{r}
ci <- .95
m <- N * p
sdm <- sqrt(N*p*(1-p))

df <- (N-n) - 1
t <- qt(ci, df)
round((m-t*sdm)/N, 3)
round((m+t*sdm)/N, 3)
```
